---
title: "DriftAndReward final"
author: "Rasmus Brostrøm"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(stats)
library(boot)
library(plotrix)
library(nlstools)
library(kableExtra)
library(latex2exp)
```

```{r}
setwd("C:/Projects/Data-driven-algorithms-for-Impulse-control-problem-Thesis")
#setwd("C:/Uni/Data-driven-algorithms-for-Impulse-control-problem-Thesis")
data <- read.csv("./SimulationData/DriftAndRewardData/DriftsAndRewards.csv")
thresholds <- read.csv("./SimulationData/DriftAndRewardData/DriftsAndRewardsThresholds.csv")
```

```{r}
data <- data %>% filter(power != "0.75")
thresholds <- thresholds %>% filter(power != "0.75")
```

```{r}
data <- data %>% mutate(exploitationTime = T-S_T,
                        DataStratNrDecisionsPerExploitationTime = dataStratNrDecisions/exploitationTime,
                        OptStratNrDecisionsPerTime = optNrDecisions/T)
```


# All plots of average regret

```{r}
avgData <- data %>%
  group_by(T, C, power, zeroVal) %>%
  summarise(avgRegret = mean(regret),
            sdRegret = sd(regret),
            varRegret = var(regret),
            avgST = mean(S_T),
            seST = std.error(S_T),
            avgDataDecisions = mean(dataStratNrDecisions),
            seDataDecisions =std.error(dataStratNrDecisions),
            avgOptDecisions = mean(optNrDecisions),
            seOptDecisions = std.error(optNrDecisions),
            avgDataDecisionsPerTime = mean(DataStratNrDecisionsPerExploitationTime),
            avgOptDecisionsPerTime = mean(OptStratNrDecisionsPerTime),
            .groups = "drop")

avgData$C = as.factor(avgData$C)
avgData$power = as.factor(avgData$power)
avgData$zeroVal = as.factor(avgData$zeroVal)
avgData$CText = paste0("C = ", avgData$C)
avgData$zeroValText = paste0("Payoff a-value = ", avgData$zeroVal)
avgData$pText = paste0("Payoff power = ", avgData$power)
```

Average cumulative regret plot

```{r}
tmpData <- avgData %>% filter(zeroVal == 0.9)

ggplot(tmpData, aes(x=T, group=CText))+
  geom_line(aes(y=avgRegret, color=CText), size=1.2)+
  #geom_hline(yintercept=0,linetype="dashed", alpha=0.5)+
  ylab("Average cumulative regret")+
  xlab("Time horizon (T)")+
  ggtitle("Average cumulative regret for drift functions")+
  scale_color_manual(values = c("C = 0.1" = "#66c2a5",
                                "C = 0.5" = "#fc8d62",
                                "C = 4" = "#8da0cb"))+
  labs(color = "Drift Slope")+
  facet_wrap(~ pText, nrow=1, scales="fixed")+
  theme_bw()+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5))+
  theme(plot.title = element_text(face = "bold", size=13),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        strip.text = element_text(size=11),
        legend.justification= c(1, 0), 
        legend.position = c(0.31, 0.74),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=11),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-6, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```


Variance of cumulative regret plot

```{r}
tmpData <- avgData %>% filter(zeroVal == 0.9)

ggplot(tmpData, aes(x=T, group=CText))+
  geom_line(aes(y=sdRegret, color=CText), size=1.2)+
  ylab("Standard deviation of cumulative regret")+
  xlab("Time horizon (T)")+
  ggtitle("Standard deviation of cumulative regret for drift functions")+
  scale_color_manual(values = c("C = 0.1" = "#66c2a5",
                                "C = 0.5" = "#fc8d62",
                                "C = 4" = "#8da0cb"))+
  labs(color = "Drift Slope")+
  facet_wrap(~ pText, nrow = 1, scales="fixed")+
  theme_bw()+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5))+
  theme(plot.title = element_text(face = "bold", size=13),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        strip.text = element_text(size=11),
        legend.justification= c(1, 0),
        legend.position = c(0.31, 0.74),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=11),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-6, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```

# Plots of average regret per time unit

```{r}
avgDataPerTime <- data %>%
  group_by(T, C, power, zeroVal) %>%
  summarise(avgRegret = mean(regret)/T,
            sdRegret = sd(regret)/T,
            varRegret = var(regret)/T,
            avgST = mean(S_T),
            seST = std.error(S_T),
            avgDataDecisions = mean(dataStratNrDecisions),
            seDataDecisions =std.error(dataStratNrDecisions),
            avgOptDecisions = mean(optNrDecisions),
            seOptDecisions = std.error(optNrDecisions),
            .groups = "drop")

avgDataPerTime$C = as.factor(avgDataPerTime$C)
avgDataPerTime$power = as.factor(avgDataPerTime$power)
avgDataPerTime$zeroVal = as.factor(avgDataPerTime$zeroVal)
avgDataPerTime$CText = paste0("C = ", avgDataPerTime$C)
avgDataPerTime$zeroValText = paste0("Payoff a-value = ", avgDataPerTime$zeroVal)
avgDataPerTime$pText = paste0("Payoff power = ", avgDataPerTime$power)
```

Average cumulative regret plot

```{r}
tmpData <- avgDataPerTime %>% filter(zeroVal == 0.9)

ggplot(tmpData, aes(x=T, group=CText))+
  geom_line(aes(y=avgRegret, color=CText), size=1.2)+
  ylab("Average cumulative regret per time unit")+
  xlab("Time horizon (T)")+
  ggtitle("Average cumulative regret per time unit for drift functions")+
  scale_color_manual(values = c("C = 0.1" = "#66c2a5",
                                "C = 0.5" = "#fc8d62",
                                "C = 4" = "#8da0cb"))+
  labs(color = "Drift Slope")+
  facet_wrap(~ pText, nrow=1, scales="free")+
  theme_bw()+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5))+
  theme(plot.title = element_text(face = "bold", size=13),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        strip.text = element_text(size=11),
        legend.justification= c(1, 0), 
        legend.position = c(0.29, 0.74),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=11),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-6, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```

Variance of cumulative regret plot

```{r}
tmpData <- avgDataPerTime %>% filter(zeroVal == 0.9)

ggplot(tmpData, aes(x=T, group=CText))+
  geom_line(aes(y=sdRegret, color=CText), size=1.2)+
  ylab("SD of cumulative regret per time unit")+
  xlab("Time horizon (T)")+
  ggtitle("Standard deviation of cumulative regret per time unit for drift functions")+
  scale_color_manual(values = c("C = 0.1" = "#66c2a5",
                                "C = 0.5" = "#fc8d62",
                                "C = 4" = "#8da0cb"))+
  labs(color = "Drift Slope")+
  facet_wrap(~ pText, nrow=1, scales="free")+
  theme_bw()+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5))+
  theme(plot.title = element_text(face = "bold", size=13),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        strip.text = element_text(size=11),
        legend.justification= c(1, 0), 
        legend.position = c(0.29, 0.74),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=11),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-6, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```


# Calculating the order of regret

```{r}
fitDriftAndRewardData <- avgData %>%
  filter(zeroVal == 0.9) %>% 
  group_by(C, power) %>% 
  summarise(
  pow=summary(nls(avgRegret ~ I(a*T^p), start=list(p=1, a=1), trace=F))$coefficients[1,1],
  powSE=summary(nls(avgRegret ~ I(a*T^p),start=list(p=1,a=1), trace=F))$coefficients[1,2],
  powSig=summary(nls(avgRegret~I(a*T^p),start=list(p=1,a=1), trace=F))$coefficients[1,4]<0.05,
  c=summary(nls(avgRegret ~ I(a*T^p), start=list(p=1, a=1), trace=F))$coefficients[2,1],
  cSE = summary(nls(avgRegret ~ I(a*T^p), start=list(p=1,a=1), trace=F))$coefficients[2,2],
  cSig = summary(nls(avgRegret~I(a*T^p),start=list(p=1,a=1), trace=F))$coefficients[2,4]<0.05,
  .groups = "drop")

fitDriftAndRewardData$pConf <- paste0(round(fitDriftAndRewardData$pow, 3), "±", round(2*fitDriftAndRewardData$powSE, 4))
fitDriftAndRewardData$cConf <- paste0(round(fitDriftAndRewardData$c, 3), "±", round(2*fitDriftAndRewardData$cSE, 4))
```

```{r}
fitDriftAndRewardData %>% 
  pivot_wider(id_cols = power, names_from = C, values_from = c(cConf, pConf)) %>%
  kable(align = rep("c", 7), col.names = NULL) %>% 
  kable_classic() %>% 
  add_header_above(c("Reward power", rep(c("Drift slope = 0.1", "Drift slope = 0.5", "Drift slope = 4"), 2))) %>% 
  add_header_above(c(" ", "Constant"=3, "Order"=3))
```

```{r}
fitDriftAndRewardData %>% 
  pivot_wider(id_cols = power, names_from = C, values_from = c(cConf)) %>%
  kable(align = rep("c", 4), col.names = NULL, linesep="", longtable=FALSE, format="latex") %>% 
  kable_classic() %>% 
  add_header_above(c("Reward power", rep(c("Drift slope = 0.1", "Drift slope = 0.5", "Drift slope = 4"), 1)))
```

```{r}
fitDriftAndRewardData %>% 
  pivot_wider(id_cols = power, names_from = C, values_from = c(pConf)) %>%
  kable(align = rep("c", 4), col.names = NULL, linesep="", longtable=FALSE, format="latex") %>% 
  kable_classic() %>% 
  add_header_above(c("Reward power", rep(c("Drift slope = 0.1", "Drift slope = 0.5", "Drift slope = 4"), 1)))
```

```{r}
fitDriftAndRewardData <- avgData %>%
  filter(zeroVal == 0.9) %>% 
  group_by(C, power) %>% 
  summarise(
  pow=summary(nls(avgRegret ~ I(T^p), start=list(p=1), trace=F))$coefficients[1,1],
  powSE=summary(nls(avgRegret ~ I(T^p),start=list(p=1), trace=F))$coefficients[1,2],
  powSig=summary(nls(avgRegret~I(T^p),start=list(p=1), trace=F))$coefficients[1,4]<0.05,
  .groups = "drop")

fitDriftAndRewardData$pConf <- paste0(round(fitDriftAndRewardData$pow, 3), "±", round(2*fitDriftAndRewardData$powSE, 4))
#fitDriftAndRewardData$cConf <- paste0(round(fitDriftAndRewardData$c, 3), "±", round(2*fitDriftAndRewardData$cSE, 4))

fitDriftAndRewardData %>% 
  pivot_wider(id_cols = power, names_from = C, values_from = c(pConf)) %>%
  kable(align = rep("c", 4), col.names = NULL) %>% 
  kable_classic() %>% 
  add_header_above(c("Reward power", "Drift slope = 0.1", "Drift slope = 0.5", "Drift slope = 4")) %>% 
  add_header_above(c(" ", "Order"=3))
```



## Plotting the fits to confirm that the fits are fine

```{r}
Cs = unique(avgData$C)
Ps = unique(avgData$power)
zeroVals = unique(avgData$zeroVal)

test3 <- data.frame()

for(c in Cs){
  for(p in Ps){
    for(z in zeroVals){
      if(c==0.5 & z==0.9 & p==0.75){
        testNew <- data.frame(C=c,
                            power=p,
                            zeroVal=z,
                            T=seq(100, 5000, by=100),
                            fittedVals = NA)
      } else{
        tmpData <- avgData %>% filter(zeroVal == z & C == c & power == p)
        m <- nls(avgRegret ~ I(a*T^p), start=list(p=1, a=1), trace=F, data = tmpData)
        fitted_values <- fitted(m)
        attributes(fitted_values)$label <- NULL
        testNew <- data.frame(C=c,
                            power=p,
                            zeroVal=z,
                            T=seq(100, 5000, by=100),
                            fittedVals = fitted_values) 
      }
      test3 <- rbind(test3, testNew)
    }
  }
}

fittedValuesDF <- merge(avgData, test3, by=c("C", "power", "T", "zeroVal"))
```

```{r}
ggplot(fittedValuesDF, aes(x=T, group=CText))+
  geom_point(aes(y=avgRegret, color=CText), shape=1, fill="white")+
  geom_line(aes(y=fittedVals), color="black", size=0.71)+
  ylab("Average cumulate regret")+
  ggtitle("Fitted average cumulative regret for drift and payoff functions")+
  labs(color = "Drift Slope")+
  facet_grid(pText ~ zeroValText, scales="free")+
  theme_bw()+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5))+
  theme(plot.margin = unit(rep(1, 4),"pt"),
        legend.justification= c(1, 0), 
        legend.position = c(0.18, 0.9),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=9),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-6, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```

```{r}
tmpData <- fittedValuesDF %>% filter(zeroVal == 0.9)

ggplot(tmpData, aes(x=T))+
  geom_point(aes(y=avgRegret, color="Actual value"), size=1.7)+
  geom_line(aes(y=fittedVals, color="Fitted value"), size=1.2)+
  scale_color_manual(values = c("Actual value" = "#66c2a5",
                                "Fitted value"="#fc8d62"))+
  ylab("Average cumulate regret")+
  xlab("Time horizon (T)")+
  ggtitle("Fitted average cumulative regret for drift functions")+
  facet_grid(pText ~ CText, scales="free")+
  theme_bw()+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5))+
  theme(plot.title = element_text(face = "bold", size=13),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        strip.text = element_text(size=11),
        legend.justification= c(1, 0), 
        legend.position = c(0.32, 0.92),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=11),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-6, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```


# Exploration times
all plots
```{r}
ggplot(avgData, aes(x=T, group=CText))+
  geom_line(aes(y=avgST, color=CText))+
  geom_line(aes(y=T^{2/3}), color="black", size=0.7)+
  ylab("Average exploration time")+
  ggtitle("Average exploration time for drift and payoff functions")+
  labs(color = "Drift Slope")+
  facet_grid(pText ~ zeroValText, scales="free")+
  theme_bw()+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5))+
  theme(plot.margin = unit(rep(1, 4),"pt"),
        legend.justification= c(1, 0), 
        legend.position = c(0.18, 0.9),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=9, face = "bold"),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-6, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```

### Fits of exploration time

```{r}
fitDriftAndRewardData <- avgData %>%
  filter(zeroVal == 0.9) %>% 
  group_by(C, power) %>% 
  summarise(
  pow=summary(nls(avgST ~ I(a*T^p), start=list(p=1, a=1), trace=F))$coefficients[1,1],
  powSE=summary(nls(avgST ~ I(a*T^p),start=list(p=1,a=1), trace=F))$coefficients[1,2],
  powSig=summary(nls(avgST~I(a*T^p),start=list(p=1,a=1), trace=F))$coefficients[1,4]<0.05,
  c=summary(nls(avgST ~ I(a*T^p), start=list(p=1, a=1), trace=F))$coefficients[2,1],
  cSE = summary(nls(avgST ~ I(a*T^p), start=list(p=1,a=1), trace=F))$coefficients[2,2],
  cSig = summary(nls(avgST~I(a*T^p),start=list(p=1,a=1), trace=F))$coefficients[2,4]<0.05,
  .groups = "drop")

fitDriftAndRewardData$pConf <- paste0(round(fitDriftAndRewardData$pow, 3), "±", round(2*fitDriftAndRewardData$powSE, 4))
fitDriftAndRewardData$cConf <- paste0(round(fitDriftAndRewardData$c, 3), "±", round(2*fitDriftAndRewardData$cSE, 4))
```

```{r}
fitDriftAndRewardData <- avgData %>%
  filter(zeroVal == 0.9) %>% 
  group_by(C, power) %>% 
  summarise(
  pow=summary(nls(avgST ~ I(T^p), start=list(p=1), trace=F))$coefficients[1,1],
  powSE=summary(nls(avgST ~ I(T^p),start=list(p=1), trace=F))$coefficients[1,2],
  powSig=summary(nls(avgST~I(T^p),start=list(p=1), trace=F))$coefficients[1,4]<0.05,
  .groups = "drop")

fitDriftAndRewardData$pConf <- paste0(round(fitDriftAndRewardData$pow, 3), "±", round(2*fitDriftAndRewardData$powSE, 4))
#fitDriftAndRewardData$cConf <- paste0(round(fitDriftAndRewardData$c, 3), "±", round(2*fitDriftAndRewardData$cSE, 4))

fitDriftAndRewardData %>% 
  pivot_wider(id_cols = power, names_from = C, values_from = c(pConf)) %>%
  kable(align = rep("c", 4), col.names = NULL) %>% 
  kable_classic() %>% 
  add_header_above(c("Reward power", "Drift slope = 0.1", "Drift slope = 0.5", "Drift slope = 4")) %>% 
  add_header_above(c(" ", "Order"=3))
```


```{r}
fitDriftAndRewardData %>% 
  pivot_wider(id_cols = power, names_from = C, values_from = c(cConf, pConf)) %>%
  kable(align = rep("c", 7), col.names = NULL) %>% 
  kable_classic() %>% 
  add_header_above(c("Reward power", rep(c("Drift slope = 0.1", "Drift slope = 0.5", "Drift slope = 4"), 2))) %>% 
  add_header_above(c(" ", "Constant"=3, "Order"=3))
```

```{r}
fitDriftAndRewardData %>% 
  pivot_wider(id_cols = power, names_from = C, values_from = c(cConf, pConf)) %>%
  kable(align = rep("c", 4), col.names = NULL, linesep="", longtable=FALSE, format="latex") %>% 
  kable_classic() %>% 
  add_header_above(c("Reward power", rep(c("Drift slope = 0.1", "Drift slope = 0.5", "Drift slope = 4"), 1)))
```


### Plots
Individual plots

```{r}
tmpData <- avgData %>% filter(zeroVal == 0.9)

ggplot(tmpData, aes(x=T))+
  geom_line(aes(y=avgST, color="Actual ST"), size=1.2)+
  geom_line(aes(y=T^{2/3}, color="Target ST"), size=1.2)+
  scale_color_manual(values = c("Actual ST" = "#66c2a5",
                                "Target ST"="#fc8d62"),
                     labels = c(TeX("Actual $S_T$"),
                                TeX("Target $S_T$")))+
  ylab(TeX("Average exploration time ( $S_T$)"))+
  xlab("Time horizon (T)")+
  ggtitle("Average exploration time for drift functions")+
  facet_grid(pText ~ CText, scales="free")+
  theme_bw()+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5))+
  theme(plot.title = element_text(face = "bold", size=13),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        strip.text = element_text(size=11),
        legend.justification= c(1, 0), 
        legend.position = c(0.15, 0.91),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=11),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-6, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```

# Number of decisions

```{r}
tmpData <- avgData %>% filter(zeroVal == 0.9)


ggplot(tmpData, aes(x=T, group=CText))+
  geom_line(aes(y=avgOptDecisions-avgDataDecisions, color=CText), size=1.2)+
  geom_hline(yintercept=0,linetype="dashed", alpha=0.5)+
  ylab("Difference in number of decisions")+
  xlab("Time horizon (T)")+
  ggtitle("Difference in number of decisions made by optimal and data-driven strategy")+
  scale_color_manual(values = c("C = 0.1" = "#66c2a5",
                                "C = 0.5" = "#fc8d62",
                                "C = 4" = "#8da0cb"))+
  labs(color = "Drift Slope")+
  facet_wrap(~pText, nrow=1, scales="fixed")+
  theme_bw()+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5))+
  theme(plot.title = element_text(face = "bold", size=13),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        strip.text = element_text(size=11),
        legend.justification= c(1, 0),
        legend.position = c(0.31, 0.74),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=11),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-6, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```

```{r}
tmpData <- avgData %>% filter(zeroVal == 0.9)


ggplot(tmpData, aes(x=T, group=CText))+
  geom_line(aes(y=avgDataDecisionsPerTime-avgOptDecisionsPerTime, color=CText), size=1.2)+
  geom_hline(yintercept=0,linetype="dashed", alpha=0.5)+
  ylab("Diff. per time in number of decisions")+
  xlab("Time horizon (T)")+
  ggtitle("Diff. in number of decisions made per time unit by optimal and data-driven strategy")+
  scale_color_manual(values = c("C = 0.1" = "#66c2a5",
                                "C = 0.5" = "#fc8d62",
                                "C = 4" = "#8da0cb"))+
  labs(color = "Drift Slope")+
  facet_wrap(~pText, nrow=1, scales="fixed")+
  theme_bw()+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5))+
  theme(plot.title = element_text(face = "bold", size=13),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        strip.text = element_text(size=11),
        legend.justification= c(1, 0),
        legend.position = c(0.31, 0.74),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=11),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-6, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```



# Looking into the thresholds

```{r}
thresholds$pText <- paste0("Payoff power = ", thresholds$power)
thresholds$CText <- paste0("C = ", thresholds$C)
thresholds$zeroValText <- paste0("Payoff a = ", thresholds$zeroVal)
```


Looking at how many thresholds were estimated at different times

```{r}
tmpData <- thresholds %>% filter(T==5000, power==1, zeroVal==0.9)

ggplot(tmpData, aes(ST))+
  geom_histogram(bins=50, color = "#000000", fill = "#1f78b4")+
  ylab("Number of estimates made")+
  xlab("Exporation time (ST)")+
  ggtitle("Number of estimates made at different exploration times for T=5000")+
  facet_wrap(~CText, nrow = 1, scales="fixed")+
  theme_bw()+
  theme(plot.title = element_text(face = "bold", size=13),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        strip.text = element_text(size=11),
        legend.justification= c(1, 0), 
        legend.position = c(0.47, 0.91),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=11),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-6, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```


```{r}
DriftAndRewardThresholds <- thresholds %>% filter(zeroVal == 0.9)

DriftAndRewardThresholds <- DriftAndRewardThresholds %>%
  mutate(cut_number = cut_number(ST, n=5),
         diffToOptimal = yhat-y_star) %>% 
  group_by(CText, cut_number, power) %>% 
  mutate(
    upperlimit = boxplot.stats(diffToOptimal)$stats[c(1, 5)][2],
    lowerlimit = boxplot.stats(diffToOptimal)$stats[c(1, 5)][1]
  ) %>% 
  ungroup()

DriftAndRewardThresholds <- DriftAndRewardThresholds %>% mutate(isLowerOutlier = diffToOptimal<lowerlimit,
                                                                isUpperOutlier = diffToOptimal>upperlimit)

loweroutliers <- DriftAndRewardThresholds %>%
  filter(diffToOptimal < lowerlimit) %>% 
  group_by(CText, cut_number) %>% 
  summarise(n = n(),
            avgDiff = mean(diffToOptimal),
            .groups = "drop"
            )

upperoutliers <- DriftAndRewardThresholds %>%
  filter(diffToOptimal > upperlimit) %>% 
  group_by(CText, cut_number) %>% 
  summarise(n = n(),
            avgDiff = mean(diffToOptimal),
            .groups = "drop"
            )

ystart_text <- DriftAndRewardThresholds %>% group_by(CText, pText) %>% 
  summarise(
    ystart_text = paste0("Opt. y = ", round(unique(y_star),2)),
    diffToOptimal = max(diffToOptimal),
    .groups = "drop"
  )

ystart_text$cut_number <- "(179,433]"


ggplot(data=DriftAndRewardThresholds, aes(cut_number, diffToOptimal))+
  geom_boxplot(aes(color=CText),outliers = F, outlier.size =0.7)+
  geom_hline(yintercept=0,linetype="dashed", alpha = 0.9)+
  ylab("Estimated threshold - Optimal threshold")+
  xlab("Exploration time interval")+
  ggtitle("Difference between estimated and optimal threshold for exploration intervals")+
  scale_color_manual(values = c("C = 0.1" = "#66c2a5",
                                "C = 0.5" = "#fc8d62",
                                "C = 4" = "#8da0cb"))+
  labs(color = "Drift Slope")+
  facet_wrap(~pText, nrow = 1, scales="free_y")+
  theme_bw()+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 4))+
  theme(plot.title = element_text(face = "bold", size=13),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        strip.text = element_text(size=11),
        legend.justification= c(1, 0), 
        legend.position = c(0.99, 0.81),
        #legend.position = "None",
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=11),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-6, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```

```{r}
loweroutliersData <- DriftAndRewardThresholds %>% filter(isLowerOutlier == TRUE)
upperoutliersData <- DriftAndRewardThresholds %>% filter(isUpperOutlier == TRUE)

outliersData <- rbind(loweroutliersData, upperoutliersData)

ggplot(data=outliersData, aes(cut_number, diffToOptimal))+
  geom_boxplot(data=loweroutliersData, aes(color=CText), outliers = T, outlier.size =0.9)+
  geom_boxplot(data=upperoutliersData, aes(color=CText), outliers = T, outlier.size =0.9)+
  geom_hline(yintercept=0,linetype="dashed", alpha = 0.5)+
  ylab("Estimated threshold - Optimal threshold")+
  xlab("Exploration time interval")+
  ggtitle("Difference between estimated and optimal threshold (a=0.99, Outliers)")+
  scale_color_manual(values = c("C = 0.1" = "#66c2a5",
                                "C = 0.5" = "#fc8d62",
                                "C = 4" = "#8da0cb"))+
  labs(color = "Drift Slope")+
  facet_wrap(~pText, nrow=2, scales="free_y")+
  theme_bw()+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 4))+
  theme(plot.title = element_text(face = "bold", size=13),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        strip.text = element_text(size=11),
        legend.justification= c(1, 0), 
        legend.position = c(0.99, 0.33),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=11),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-6, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```


## All thresholds together
```{r}
thresholds <- thresholds %>%
  mutate(cut_number = cut_number(ST, n=5),
         diffToOptimal = yhat-y_star) %>% 
  group_by(CText, cut_number, power, zeroVal) %>% 
  mutate(
    upperlimit = boxplot.stats(diffToOptimal)$stats[c(1, 5)][2],
    lowerlimit = boxplot.stats(diffToOptimal)$stats[c(1, 5)][1]
  ) %>% 
  ungroup()

thresholds <- thresholds %>% mutate(isLowerOutlier = diffToOptimal<lowerlimit,
                                    isUpperOutlier = diffToOptimal>upperlimit)

loweroutliers <- thresholds %>%
  filter(diffToOptimal < lowerlimit) %>% 
  group_by(CText, cut_number, power, zeroVal) %>% 
  summarise(n = n(),
            avgDiff = mean(diffToOptimal),
            .groups = "drop"
            )

upperoutliers <- thresholds %>%
  filter(diffToOptimal > upperlimit) %>% 
  group_by(CText, cut_number, power, zeroVal) %>% 
  summarise(n = n(),
            avgDiff = mean(diffToOptimal),
            .groups = "drop"
            )

ystart_text <- thresholds %>% group_by(CText, cut_number, power, zeroVal) %>% 
  summarise(
    ystart_text = paste0("Opt. y = ", round(unique(y_star),2)),
    diffToOptimal = max(diffToOptimal),
    .groups = "drop"
  )

ystart_text$cut_number <- "(179,433]"


ggplot(data=thresholds, aes(cut_number, diffToOptimal))+
  geom_boxplot(aes(color=CText), outliers = T, outlier.size = 0.9)+
  geom_hline(yintercept=0,linetype="dashed", alpha = 0.5)+
  ylab("Estimated threshold - Optimal threshold")+
  xlab("Exploration time interval")+
  ggtitle("Difference between estimated and optimal threshold for exploration intervals")+
  scale_color_manual(values = c("Drift slope = 0.1" = "#66c2a5",
                                "Drift slope = 0.5" = "#fc8d62",
                                "Drift slope = 4" = "#8da0cb"))+
  labs(color = "Drift Slope")+
  facet_grid(pText~zeroValText, scales="free")+
  theme_bw()+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5))+
  theme(plot.title = element_text(face = "bold", size=13),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        strip.text = element_text(size=11),
        legend.justification= c(1, 0), 
        legend.position = c(0.99, 0.15),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=11),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-6, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```


## Better thresholds distribution

```{r}
DriftAndRewardThresholds <- thresholds %>% filter(zeroVal == 0.9)

DriftAndRewardThresholds <- DriftAndRewardThresholds %>%
  mutate(cut_number = cut_number(ST, n=5),
         diffToOptimal = yhat-y_star) %>% 
  group_by(CText, cut_number, power) %>% 
  mutate(
    upperlimit = boxplot.stats(diffToOptimal)$stats[c(1, 5)][2],
    lowerlimit = boxplot.stats(diffToOptimal)$stats[c(1, 5)][1]
  ) %>% 
  ungroup()

DriftAndRewardThresholds <- DriftAndRewardThresholds %>% mutate(isLowerOutlier = diffToOptimal<lowerlimit,
                                                                isUpperOutlier = diffToOptimal>upperlimit)

loweroutliers <- DriftAndRewardThresholds %>%
  filter(diffToOptimal < lowerlimit) %>% 
  group_by(CText, cut_number) %>% 
  summarise(n = n(),
            avgDiff = mean(diffToOptimal),
            .groups = "drop"
            )

upperoutliers <- DriftAndRewardThresholds %>%
  filter(diffToOptimal > upperlimit) %>% 
  group_by(CText, cut_number) %>% 
  summarise(n = n(),
            avgDiff = mean(diffToOptimal),
            .groups = "drop"
            )

ystart_text <- DriftAndRewardThresholds %>% group_by(CText, pText) %>% 
  summarise(
    ystart_text = paste0("Opt. y = ", round(unique(y_star),2)),
    diffToOptimal = max(diffToOptimal),
    .groups = "drop"
  )

ystart_text$cut_number <- "(179,433]"


ggplot(data=DriftAndRewardThresholds, aes(cut_number, diffToOptimal))+
  geom_boxplot(aes(color=CText),outliers = F, outlier.size =0.7)+
  geom_hline(yintercept=0,linetype="dashed", alpha = 0.9)+
  ylab("Estimated threshold - Optimal threshold")+
  xlab("Exploration time interval")+
  ggtitle("Difference between estimated and optimal threshold over exploration intervals")+
  scale_color_manual(values = c("C = 0.1" = "#66c2a5",
                                "C = 0.5" = "#fc8d62",
                                "C = 4" = "#8da0cb"))+
  # labs(color = "Drift Slope")+
  facet_wrap(pText ~ CText, ncol=3, scales="free_y")+
  theme_bw()+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 3))+
  theme(plot.title = element_text(face = "bold", size=13),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        strip.text = element_text(size=11),
        legend.justification= c(1, 0), 
        #legend.position = c(0.99, 0.33),
        legend.position = "None",
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=11),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-6, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```

```{r}
loweroutliersData <- DriftAndRewardThresholds %>% filter(isLowerOutlier == TRUE)
upperoutliersData <- DriftAndRewardThresholds %>% filter(isUpperOutlier == TRUE)

outliersData <- rbind(loweroutliersData, upperoutliersData)

ggplot(data=outliersData, aes(cut_number, diffToOptimal))+
  geom_boxplot(data=loweroutliersData, aes(color=CText), outliers = T, outlier.size =0.9)+
  geom_boxplot(data=upperoutliersData, aes(color=CText), outliers = T, outlier.size =0.9)+
  geom_hline(yintercept=0,linetype="dashed", alpha = 0.5)+
  ylab("Estimated threshold - Optimal threshold")+
  xlab("Exploration time interval")+
  ggtitle("Difference between estimated and optimal threshold over exploration intervals (Outliers)")+
  scale_color_manual(values = c("C = 0.1" = "#66c2a5",
                                "C = 0.5" = "#fc8d62",
                                "C = 4" = "#8da0cb"))+
  labs(color = "Drift Slope")+
  facet_wrap(pText ~ CText, ncol=3, scales="free_y", drop = FALSE)+
  theme_bw()+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 4))+
  theme(plot.title = element_text(face = "bold", size=13),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        strip.text = element_text(size=11),
        legend.justification= c(1, 0), 
        legend.position = "None",
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=11),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-6, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```

