---
title: "ExplorationChanges"
author: "Rasmus Brostrøm"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(stats)
library(boot)
library(plotrix)
library(nlstools)
library(kableExtra)
```

```{r}
#setwd("C:/Projects/Data-driven-algorithms-for-Impulse-control-problem-Thesis")
setwd("C:/Uni/Data-driven-algorithms-for-Impulse-control-problem-Thesis")
ExplorationFormsData <- read.csv("./SimulationData/ExplorationData/ExplorationForms.csv")
```


# Exploration time
In the algorithm it is given that the exploration time should be of the form:
$$
S_T = T^{2/3}
$$
to balance the regret from exploring and the regret from exploiting. We will now look at how changing the order of the exploration time affects the average regret. To do so we will look at 5 different exploration formulas, where each exploration formula is simulated 100 times for the time horizons $T\in \{100, 200, \dots, 5000\}$ with the four combinations of drift and payoff function given by the the linear drift function:
$$
b(x) = -Cx, \quad C\in \{0.5, 4\}
$$
and the payoff function:
$$
g(x) = 0.9-|1-x|^p, \quad p\in \{1, 5\}
$$
The exploration forms that we are looking at are:
$$
  S_T = 2\cdot(\sqrt{2\cdot\sqrt{T}+1} + \sqrt{T}+1)\\
  S_T = T^{k}, \quad k\in \{1/4, \, 1/3, \, 1/2, \, 2/3\}
$$


```{r}
avgExplorationData <- ExplorationFormsData %>% group_by(T, C, power, ST_form) %>% 
                          summarise(avgRegret = mean(regret),
                                    seRegret = std.error(regret),
                                    varRegret = var(regret),
                                    sdRegret = sd(regret),
                                    avgST = mean(S_T),
                                    seST = std.error(S_T),
                                    avgDataDecisions = mean(dataStratNrDecisions),
                                    seDataDecisions =std.error(dataStratNrDecisions),
                                    avgOptDecisions = mean(optNrDecisions),
                                    seOptDecisions = std.error(optNrDecisions),
                                    .groups = "drop")

avgExplorationData$C = as.factor(avgExplorationData$C)
avgExplorationData$power = as.factor(avgExplorationData$power)
avgExplorationData$ST_form = as.factor(avgExplorationData$ST_form)
avgExplorationData$C_text = paste0("Drift slope = ", avgExplorationData$C)
avgExplorationData$P_text = paste0("Payoff power = ", avgExplorationData$power)
```


```{r}
avgExplorationDataNew <- avgExplorationData %>% filter(ST_form != "T^(3/4)")
ggplot(avgExplorationDataNew, aes(x=T, group=ST_form))+
  geom_line(aes(y=avgRegret, color=ST_form))+
  labs(title = "Average regret for Exploration forms",
       y = "Average regret",
       x = "Time horizon (T)",
       color = "Exploration: ")+
  facet_grid(P_text ~ C_text, scales = "free")+
  theme(legend.position="bottom")
```


Lets also look at the standard deviation of the regret to see how changing the exploration times affects the stability of the regret

```{r}
ggplot(avgExplorationDataNew, aes(x=T, group=ST_form))+
  geom_line(aes(y=sdRegret, color=ST_form))+
  labs(title = "SD of regret for Exploration forms",
       y = "SD of regret",
       x = "Time horizon (T)",
       color = "Exploration: ")+
  facet_grid(P_text ~ C_text, scales = "free")+
  theme(legend.position="bottom")
```

## Lets confirm that the exploration times actually fit the corresponding exploration forms:

```{r}
avgExplorationTime <- ExplorationFormsData %>% group_by(T, ST_form) %>% 
  summarise(avgST = mean(S_T),
            .groups = "drop")

avgExplorationTime %>% filter(ST_form == "2*(sqrt(2*sqrt(T)+1) + sqrt(T) + 1)") %>% 
  ggplot(aes(x=T))+
  geom_line(aes(y=avgST))+
  geom_line(aes(y=2*(sqrt(2*sqrt(T)+1)+sqrt(T)+1), color="red"))+
  ylab("Average exploration time")+
  ggtitle("Average exploration time for 2*(sqrt(2*sqrt(T)+1) + sqrt(T) + 1)")+
  theme(legend.position="none")

avgExplorationTime %>% filter(ST_form == "T^(1/4)") %>% 
  ggplot(aes(x=T))+
  geom_line(aes(y=avgST))+
  geom_line(aes(y=T^(1/4), color="red"))+
  ylab("Average exploration time")+
  ggtitle("Average exploration time for T^(1/4)")+
  theme(legend.position="none")

avgExplorationTime %>% filter(ST_form == "T^(1/3)") %>% 
  ggplot(aes(x=T))+
  geom_line(aes(y=avgST))+
  geom_line(aes(y=T^(1/3), color="red"))+
  ylab("Average exploration time")+
  ggtitle("Average exploration time for T^(1/3)")+
  theme(legend.position="none")

avgExplorationTime %>% filter(ST_form == "T^(1/2)") %>% 
  ggplot(aes(x=T))+
  geom_line(aes(y=avgST))+
  geom_line(aes(y=T^(1/2), color="red"))+
  ylab("Average exploration time")+
  ggtitle("Average exploration time for T^(1/2)")+
  theme(legend.position="none")

avgExplorationTime %>% filter(ST_form == "T^(2/3)") %>% 
  ggplot(aes(x=T))+
  geom_line(aes(y=avgST))+
  geom_line(aes(y=T^(2/3), color="red"))+
  ylab("Average exploration time")+
  ggtitle("Average exploration time for T^(2/3)")+
  theme(legend.position="none")
```


## Difference in number of decisions:
```{r}
ggplot(avgExplorationDataNew, aes(x=T, group=ST_form))+
  geom_line(aes(y=avgOptDecisions-avgDataDecisions, color=ST_form))+
  labs(title = "Difference in number of decisions for Exploration forms",
       y = "Difference in number of decisions",
       x = "Time horizon (T)",
       color = "Exploration: ")+
  facet_grid(P_text ~ C_text, scales = "free")+
  theme(legend.position="bottom")
```

