---
title: "ExplorationChanges"
author: "Rasmus Brostrøm"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(stats)
library(boot)
library(plotrix)
library(nlstools)
library(kableExtra)
library(latex2exp)
library(ggh4x)
```

```{r}
setwd("C:/Projects/Data-driven-algorithms-for-Impulse-control-problem-Thesis")
#setwd("C:/Uni/Data-driven-algorithms-for-Impulse-control-problem-Thesis")
data <- read.csv("./SimulationData/ExplorationData/ExplorationFormsStrategiesData.csv")
thresholds <- read.csv("./SimulationData/ExplorationData/ExplorationFormsStrategiesThresholdData.csv")
```

```{r}
data <- data %>% filter(ST_form != "T^(3/4)" & ST_form != "2*(sqrt(2*sqrt(T)+1) + sqrt(T) + 1)")

data <- data %>% mutate(exploitationTime = T-S_T,
                        DataStratNrDecisionsPerExploitationTime = dataStratNrDecisions/exploitationTime,
                        OptStratNrDecisionsPerTime = optNrDecisions/T)
```

```{r}
thresholds <- thresholds %>% filter(ST_form != "T^(3/4)" & ST_form != "2*(sqrt(2*sqrt(T)+1) + sqrt(T) + 1)")
```



# Exploration time
In the algorithm it is given that the exploration time should be of the form:

$$
S_T = T^{2/3}
$$

to balance the regret from exploring and the regret from exploiting. We will now look at how changing the order of the exploration time affects the average regret. To do so we will look at 5 different exploration formulas, where each exploration formula is simulated 100 times for the time horizons $T\in \{100, 200, \dots, 5000\}$ with the four combinations of drift and payoff function given by the the linear drift function:

$$
b(x) = -Cx, \quad C\in \{0.5, 4\}
$$

and the payoff function:

$$
g(x) = 0.9-|1-x|^p, \quad p\in \{1, 5\}
$$

The exploration forms that we are looking at are:

$$
  S_T = 2\cdot(\sqrt{2\cdot\sqrt{T}+1} + \sqrt{T}+1)\\
  S_T = T^{k}, \quad k\in \{1/4, \, 1/3, \, 1/2, \, 2/3\}
$$


```{r}
avgData <- data %>% group_by(T, C, power, ST_form) %>% 
                          summarise(avgRegret = mean(regret),
                                    seRegret = std.error(regret),
                                    varRegret = var(regret),
                                    sdRegret = sd(regret),
                                    avgST = mean(S_T),
                                    seST = std.error(S_T),
                                    avgDataDecisions = mean(dataStratNrDecisions),
                                    seDataDecisions =std.error(dataStratNrDecisions),
                                    avgOptDecisions = mean(optNrDecisions),
                                    seOptDecisions = std.error(optNrDecisions),
                                    avgDataDecisionsPerTime = mean(DataStratNrDecisionsPerExploitationTime),
                                    avgOptDecisionsPerTime = mean(OptStratNrDecisionsPerTime),
                                    .groups = "drop")

avgData$C = as.factor(avgData$C)
avgData$power = as.factor(avgData$power)
avgData$ST_form = factor(avgData$ST_form, levels = c("T^(1/4)", "T^(1/3)", "T^(1/2)", "T^(2/3)"))
avgData$CText = paste0("C = ", avgData$C)
avgData$pText = paste0("Payoff power = ", avgData$power)
```

```{r}
unique(avgData$ST_form)
```



```{r}

ggplot(avgData, aes(x=T, group=ST_form))+
  geom_line(aes(y=avgRegret, color=ST_form), size=1.2)+
  labs(title = "Average cumulative regret for different orders of exploration",
       y = "Average cumulative regret",
       x = "Time horizon (T)",
       color = "Exploration order")+
  ggh4x::facet_grid2(pText ~ CText, scales = "free_y", independent = "y")+
  scale_color_manual(values = c("T^(1/4)" = "#4477AA",
                                "T^(1/3)" = "#EE6677",
                                "T^(1/2)" = "#228833",
                                "T^(2/3)" = "#CCBB44"),
                     labels = c(TeX("$S_T = T^{1/4}$"),
                                TeX("$S_T = T^{1/3}$"),
                                TeX("$S_T = T^{1/2}$"),
                                TeX("$S_T = T^{2/3}$")))+
  theme_bw()+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5))+
  theme(plot.title = element_text(face="bold",size=13),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        strip.text = element_text(size=11),
        legend.justification= c(1, 0), 
        legend.position = c(0.15, 0.77),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=11),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-3, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```


Lets also look at the standard deviation of the regret to see how changing the exploration times affects the stability of the regret

```{r}
ggplot(avgData, aes(x=T, group=ST_form))+
  geom_line(aes(y=sdRegret, color=ST_form), size=1.2)+
  labs(title = "Standard deviation of cumulative regret for different orders of exploration",
       y = "Standard deviation of cumulative regret",
       x = "Time horizon (T)",
       color = "Exploration order")+
  ggh4x::facet_grid2(pText ~ CText, scales = "free_y", independent = "y")+
  scale_color_manual(values = c("T^(1/4)" = "#4477AA",
                                "T^(1/3)" = "#EE6677",
                                "T^(1/2)" = "#228833",
                                "T^(2/3)" = "#CCBB44"),
                     labels = c(TeX("$S_T = T^{1/4}$"),
                                TeX("$S_T = T^{1/3}$"),
                                TeX("$S_T = T^{1/2}$"),
                                TeX("$S_T = T^{2/3}$")))+
  theme_bw()+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 4))+
  theme(plot.title = element_text(face="bold",size=13),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        strip.text = element_text(size=11),
        legend.justification= c(1, 0), 
        legend.position = c(0.15, 0.77),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=11),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-3, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```

# Fitting average cumulative regret

```{r}
fitDriftAndRewardData <- avgData %>%
  filter(pText == "Payoff power = 5") %>% 
  group_by(ST_form, CText) %>% 
  summarise(
  pow=summary(nls(avgRegret ~ I(a*T^p), start=list(p=1, a=1), trace=F))$coefficients[1,1],
  powSE=summary(nls(avgRegret ~ I(a*T^p),start=list(p=1,a=1), trace=F))$coefficients[1,2],
  powSig=summary(nls(avgRegret~I(a*T^p),start=list(p=1,a=1), trace=F))$coefficients[1,4]<0.05,
  c=summary(nls(avgRegret ~ I(a*T^p), start=list(p=1, a=1), trace=F))$coefficients[2,1],
  cSE = summary(nls(avgRegret ~ I(a*T^p), start=list(p=1,a=1), trace=F))$coefficients[2,2],
  cSig = summary(nls(avgRegret~I(a*T^p),start=list(p=1,a=1), trace=F))$coefficients[2,4]<0.05,
  .groups = "drop")

fitDriftAndRewardData$pConf <- paste0(round(fitDriftAndRewardData$pow, 3), "±", round(2*fitDriftAndRewardData$powSE, 4))
fitDriftAndRewardData$cConf <- paste0(round(fitDriftAndRewardData$c, 3), "±", round(2*fitDriftAndRewardData$cSE, 4))
```

```{r}
fitDriftAndRewardData %>% 
  pivot_wider(id_cols = ST_form, names_from = CText, values_from = c(cConf, pConf)) %>%
  kable(align = rep("c", 5), col.names = NULL) %>% 
  kable_classic() %>% 
  add_header_above(c("ST_form", rep(c("C = 0.5", "C = 4"), 2))) %>% 
  add_header_above(c(" ", "Constant"=2, "Order"=2))
```

```{r}
fitDriftAndRewardData %>% 
  pivot_wider(id_cols = ST_form, names_from = CText, values_from = c(cConf, pConf)) %>%
  kable(align = rep("c", 5), col.names = NULL, linesep="", longtable=FALSE, format="latex") %>% 
  kable_classic() %>% 
  add_header_above(c("ST_form", rep(c("C = 0.5", "C = 4"), 2))) %>% 
  add_header_above(c(" ", "Constant"=2, "Order"=2))
```

### Plotting the fits

```{r}
As = unique(avgData$CText)
Sigmas = unique(avgData$ST_form)
powers = unique(avgData$pText)

test3 <- data.frame()

for(c in As){
  for(p in powers){
    for(z in Sigmas){
      tmpData <- avgData %>% filter(ST_form == z & CText == c & pText == p)
      m <- nls(avgRegret ~ I(a*T^p), start=list(p=1, a=1), trace=F, data = tmpData)
      fitted_values <- fitted(m)
      attributes(fitted_values)$label <- NULL
      testNew <- data.frame(CText=c,
                            pText=p,
                            ST_form=z,
                            T=seq(100, 5000, by=100),
                            fittedVals = fitted_values) 

      test3 <- rbind(test3, testNew)
    }
  }
}

fittedValuesDF <- merge(avgData, test3, by=c("CText", "pText", "T", "ST_form"))
```

```{r}
#tmpData <- fittedValuesDF %>% filter(aText == "a_s = 1e-06")
#tmpData <- fittedValuesDF %>% filter(aText == "a_s = 0.5a")
#tmpData <- fittedValuesDF %>% filter(aText == "a_s = a")
#tmpData <- fittedValuesDF %>% filter(aText == "a_s = 2a")
tmpData <- fittedValuesDF %>% filter(pText == "Payoff power = 5")

ggplot(tmpData, aes(x=T))+
  geom_point(aes(y=avgRegret, color="Actual value"), size=1.7)+
  geom_line(aes(y=fittedVals, color="Fitted value"), size=1.2)+
  scale_color_manual(values = c("Actual value" = "#66c2a5",
                                "Fitted value"="#fc8d62"))+
  ylab("Average cumulate regret")+
  xlab("Time horizon (T)")+
  ggtitle(TeX("\\textbf{Fitted average cumulative regret with $p=5$}"))+
  ggh4x::facet_grid2(ST_form ~ CText, scales="free_y", independent = "y")+
  theme_bw()+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5))+
  theme(plot.title = element_text(face = "bold", size=13),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        strip.text = element_text(size=11),
        legend.justification= c(1, 0), 
        legend.position = c(0.17, 0.76),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=11),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-6, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```

# Exploration times

```{r}
tmpData <- avgData %>% filter(ST_form == "T^(2/3)")

ggplot(tmpData, aes(x=T))+
  geom_line(aes(y=avgST, color="Actual ST"), size=1.2)+
  geom_line(aes(y=T^{2/3}, color="Target ST"), size=1.2)+
  scale_color_manual(values = c("Actual ST" = "#4477AA",
                                "Target ST"="#EE6677"))+
  ylab("Average exploration time (ST)")+
  xlab("Time horizon (T)")+
  ggtitle(TeX("\\textbf{Average exploration time for $S_T = T^{2/3}$}"))+
  #ggh4x::facet_grid2(pText ~ CText, scales="free_y", independent = "y")+
  facet_grid(pText ~ CText, scales="fixed")+
  theme_bw()+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5))+
  theme(plot.title = element_text(face = "bold", size=13),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        strip.text = element_text(size=11),
        legend.justification= c(1, 0), 
        legend.position = c(0.15, 0.88),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=11),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-6, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```

## Calculating fits

```{r}
fitDriftAndRewardData <- avgData %>%
  filter(pText == "Payoff power = 1") %>% 
  group_by(ST_form, CText) %>% 
  summarise(
  pow=summary(nls(avgST ~ I(a*T^p), start=list(p=1, a=1), trace=F))$coefficients[1,1],
  powSE=summary(nls(avgST ~ I(a*T^p),start=list(p=1,a=1), trace=F))$coefficients[1,2],
  powSig=summary(nls(avgST~I(a*T^p),start=list(p=1,a=1), trace=F))$coefficients[1,4]<0.05,
  c=summary(nls(avgST ~ I(a*T^p), start=list(p=1, a=1), trace=F))$coefficients[2,1],
  cSE = summary(nls(avgST ~ I(a*T^p), start=list(p=1,a=1), trace=F))$coefficients[2,2],
  cSig = summary(nls(avgST~I(a*T^p),start=list(p=1,a=1), trace=F))$coefficients[2,4]<0.05,
  .groups = "drop")

fitDriftAndRewardData$pConf <- paste0(round(fitDriftAndRewardData$pow, 3), "±", round(2*fitDriftAndRewardData$powSE, 4))
fitDriftAndRewardData$cConf <- paste0(round(fitDriftAndRewardData$c, 3), "±", round(2*fitDriftAndRewardData$cSE, 4))
```

```{r}
fitDriftAndRewardData %>% 
  pivot_wider(id_cols = ST_form, names_from = CText, values_from = c(cConf, pConf)) %>%
  kable(align = rep("c", 5), col.names = NULL) %>% 
  kable_classic() %>% 
  add_header_above(c("ST_form", rep(c("C = 0.5", "C = 4"), 2))) %>% 
  add_header_above(c(" ", "Constant"=2, "Order"=2))
```

```{r}
fitDriftAndRewardData %>% 
  pivot_wider(id_cols = ST_form, names_from = CText, values_from = c(cConf, pConf)) %>%
  kable(align = rep("c", 5), col.names = NULL, linesep="", longtable=FALSE, format="latex") %>% 
  kable_classic() %>% 
  add_header_above(c("ST_form", rep(c("C = 0.5", "C = 4"), 2))) %>% 
  add_header_above(c(" ", "Constant"=2, "Order"=2))
```

# Number of decisions

```{r}
ggplot(avgData, aes(x=T, group=ST_form))+
  geom_line(aes(y=avgDataDecisionsPerTime-avgOptDecisionsPerTime, color=ST_form), size=1.2)+
  geom_hline(yintercept=0,linetype="dashed")+
  ylab("Difference in number of decisions per time")+
  xlab("Time horizon (T)")+
  ggtitle("Diff. in number of decisions made per time unit by optimal and data-driven strategy")+
  scale_color_manual(values = c("T^(1/4)" = "#4477AA",
                                "T^(1/3)" = "#EE6677",
                                "T^(1/2)" = "#228833",
                                "T^(2/3)" = "#CCBB44"),
                     labels = c(TeX("$S_T = T^{1/4}$"),
                                TeX("$S_T = T^{1/3}$"),
                                TeX("$S_T = T^{1/2}$"),
                                TeX("$S_T = T^{2/3}$")))+
  facet_grid(pText ~ CText, scales="free")+
  theme_bw()+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5))+
  theme(plot.title = element_text(face = "bold", size=13),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        strip.text = element_text(size=11),
        legend.justification= c(1, 0), 
        legend.position = c(0.14, 0.53),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=11),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-6, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```

# Thresholds

```{r}
thresholds$C = as.factor(thresholds$C)
thresholds$power = as.factor(thresholds$power)
thresholds$ST_form = factor(thresholds$ST_form, levels = c("T^(1/4)", "T^(1/3)", "T^(1/2)", "T^(2/3)"))
thresholds$CText = paste0("C = ", thresholds$C)
thresholds$pText = paste0("Payoff power = ", thresholds$power)
```

```{r}
tmp <- thresholds %>% filter(T==5000, power==1)

ggplot(tmp, aes(ST))+
  geom_histogram(bins=50, color = "#000000", fill = "#1f78b4")+
  ylab("Number of estimates made")+
  xlab("Exporation time (ST)")+
  ggtitle("Number of estimates made at different exploration times with T=5000")+
  facet_grid(CText~ST_form, scales="fixed")+
  theme_bw()+
  theme(plot.title = element_text(face = "bold", size=13),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        strip.text = element_text(size=11),
        legend.justification= c(1, 0), 
        legend.position = c(0.47, 0.91),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=11),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-6, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```

```{r}
thresholds <- thresholds %>%
  mutate(cut_number = cut_number(ST, n=5),
         diffToOptimal = yhat-y_star) %>% 
  group_by(pText, cut_number, ST_form, CText) %>% 
  mutate(
    upperlimit = boxplot.stats(diffToOptimal)$stats[c(1, 5)][2],
    lowerlimit = boxplot.stats(diffToOptimal)$stats[c(1, 5)][1]
  ) %>% 
  ungroup()

thresholds <- thresholds %>%
  mutate(isLowerOutlier = diffToOptimal<lowerlimit,
         isUpperOutlier = diffToOptimal>upperlimit,
         isOutlier = diffToOptimal<lowerlimit| diffToOptimal>upperlimit)

loweroutliers <- thresholds %>%
  filter(diffToOptimal < lowerlimit) %>% 
  group_by(pText, cut_number, ST_form, CText) %>% 
  summarise(n = n(),
            avgDiff = mean(diffToOptimal),
            .groups = "drop"
            )

upperoutliers <- thresholds %>%
  filter(diffToOptimal > upperlimit) %>% 
  group_by(pText, cut_number, ST_form, CText) %>% 
  summarise(n = n(),
            avgDiff = mean(diffToOptimal),
            .groups = "drop"
            )

ystart_text <- thresholds %>% group_by(pText, cut_number, ST_form, CText) %>% 
  summarise(
    ystart_text = paste0("Opt. y = ", round(unique(y_star),2)),
    diffToOptimal = max(diffToOptimal),
    .groups = "drop"
  )

ystart_text$cut_number <- "(179,433]"


ggplot(data=thresholds, aes(cut_number, diffToOptimal))+
  geom_boxplot(aes(color=ST_form), outliers = F, outlier.size = 0.7, position = position_dodge2(preserve = "single"))+
  geom_hline(yintercept=0,linetype="dashed", alpha=0.5)+
  ylab("Estimated threshold - Optimal threshold")+
  xlab("Exploration time interval")+
  ggtitle("Difference between estimated and optimal threshold for exploration orders")+
  scale_color_manual(values = c("T^(1/4)" = "#4477AA",
                                "T^(1/3)" = "#EE6677",
                                "T^(1/2)" = "#228833",
                                "T^(2/3)" = "#CCBB44"),
                     labels = c(TeX("$S_T = T^{1/4}$"),
                                TeX("$S_T = T^{1/3}$"),
                                TeX("$S_T = T^{1/2}$"),
                                TeX("$S_T = T^{2/3}$")))+
  ggh4x::facet_grid2(pText ~ CText, scales="free_y", independent = "y")+
  theme_bw()+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 4))+
  theme(plot.title = element_text(face = "bold", size=13),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        strip.text = element_text(size=11),
        legend.justification= c(1, 1), 
        legend.position = c(0.98, 0.98),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=11),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-6, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```


```{r}
loweroutliersData <- thresholds %>% filter(isLowerOutlier == TRUE)
upperoutliersData <- thresholds %>% filter(isUpperOutlier == TRUE)

outliersData <- rbind(loweroutliersData, upperoutliersData)

negativeOutliers <- thresholds %>% filter(isOutlier == TRUE & diffToOptimal < 0)
positiveOutliers <- thresholds %>% filter(isOutlier == TRUE & diffToOptimal > 0)

outliersData2 <- rbind(negativeOutliers, positiveOutliers)

ggplot(data=outliersData, aes(cut_number, diffToOptimal))+
  geom_boxplot(data=loweroutliersData, aes(color=ST_form),
               outliers = T, outlier.size = 0.9, position = position_dodge2(preserve = "single"))+
  geom_boxplot(data=upperoutliersData, aes(color=ST_form),
               outliers = T, outlier.size = 0.9, position = position_dodge2(preserve = "single"))+
  geom_hline(yintercept=0,linetype="dashed", alpha=0.5)+
  ylab("Estimated threshold - Optimal threshold")+
  xlab("Exploration time interval")+
  ggtitle("Difference between estimated and optimal threshold for exploration orders (outliers)")+
  scale_color_manual(values = c("T^(1/4)" = "#4477AA",
                                "T^(1/3)" = "#EE6677",
                                "T^(1/2)" = "#228833",
                                "T^(2/3)" = "#CCBB44"),
                     labels = c(TeX("$S_T = T^{1/4}$"),
                                TeX("$S_T = T^{1/3}$"),
                                TeX("$S_T = T^{1/2}$"),
                                TeX("$S_T = T^{2/3}$")))+
  ggh4x::facet_grid2(pText ~ CText, scales="free_y", independent = "y")+
  theme_bw()+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5))+
  theme(plot.title = element_text(face = "bold", size=13),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        strip.text = element_text(size=11),
        legend.justification= c(1, 1), 
        legend.position = c(0.98, 0.98),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=11),
        legend.margin = margin(0, 0, 0, 0),
        legend.key.spacing.x = unit(0, "pt"),
        legend.key.spacing.y = unit(-6, "pt"),
        legend.spacing.y = unit(-5, "pt"),
        legend.box.spacing = unit(0, "pt"),
        legend.background = element_rect(fill=alpha(0.0001)))
```



## Lets confirm that the exploration times actually fit the corresponding exploration forms:

```{r}
avgExplorationTime <- ExplorationFormsData %>% group_by(T, ST_form) %>% 
  summarise(avgST = mean(S_T),
            .groups = "drop")

avgExplorationTime %>% filter(ST_form == "2*(sqrt(2*sqrt(T)+1) + sqrt(T) + 1)") %>% 
  ggplot(aes(x=T))+
  geom_line(aes(y=avgST))+
  geom_line(aes(y=2*(sqrt(2*sqrt(T)+1)+sqrt(T)+1), color="red"))+
  ylab("Average exploration time")+
  ggtitle("Average exploration time for 2*(sqrt(2*sqrt(T)+1) + sqrt(T) + 1)")+
  theme(legend.position="none")

avgExplorationTime %>% filter(ST_form == "T^(1/4)") %>% 
  ggplot(aes(x=T))+
  geom_line(aes(y=avgST))+
  geom_line(aes(y=T^(1/4), color="red"))+
  ylab("Average exploration time")+
  ggtitle("Average exploration time for T^(1/4)")+
  theme(legend.position="none")

avgExplorationTime %>% filter(ST_form == "T^(1/3)") %>% 
  ggplot(aes(x=T))+
  geom_line(aes(y=avgST))+
  geom_line(aes(y=T^(1/3), color="red"))+
  ylab("Average exploration time")+
  ggtitle("Average exploration time for T^(1/3)")+
  theme(legend.position="none")

avgExplorationTime %>% filter(ST_form == "T^(1/2)") %>% 
  ggplot(aes(x=T))+
  geom_line(aes(y=avgST))+
  geom_line(aes(y=T^(1/2), color="red"))+
  ylab("Average exploration time")+
  ggtitle("Average exploration time for T^(1/2)")+
  theme(legend.position="none")

avgExplorationTime %>% filter(ST_form == "T^(2/3)") %>% 
  ggplot(aes(x=T))+
  geom_line(aes(y=avgST))+
  geom_line(aes(y=T^(2/3), color="red"))+
  ylab("Average exploration time")+
  ggtitle("Average exploration time for T^(2/3)")+
  theme(legend.position="none")
```




